Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-19 6-ModelPresentation.tex
Updates from Overleaf

\todo{Augmenter la taille des fontes}

@@

The challenge describes in a second part a Software engineering process for fictional Acme company. Base metamodel as described in previous section is too generic to capture all domain-specific aspects of this use case. We choose to complete the architectual hierarchy with a specific metamodel, specific to Acme software development process, as shown in figure \ref{fig:MultilevelArchitecture}. \textit{Acme metamodel} inherits and specializes base metamodel, and \textit{Acme model} is defined as an instance of \textit{Acme metamodel}.

>>>>

@@

The challenge describes in a second part a Software engineering process for fictional Acme company. Base metamodel as described in previous section is too generic to capture all domain-specific aspects of this use case. We choose to complete the architectual hierarchy with a specific metamodel, specific to Acme software development process, as shown in figure \ref{fig:AcmeArchitecture}. \textit{Acme metamodel} inherits and specializes base metamodel, and \textit{Acme model} is defined as an instance of \textit{Acme metamodel}.

\begin{figure}
 \centering
    \includegraphics[width=1.0 \textwidth]{Figures/AcmeArchitecture.pdf}
     \caption{Acme software development process architecture}
    \label{fig:AcmeArchitecture}
\end{figure}
